An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-15 evaluation.tex
Add citiation into Section 2

We evaluated the correctness and performance of running, packaging, and re-running the TauRoast application using Parrot and PTU.
To do this, the application was first executed directly, its execution time and output were recorded. Then the application was executed under Parrot and PTU, and a self-contained package was created for each case. Finally, the application was re-executed using the package. The time overhead of each execution and re-execution was collected and compared with the recorded reference.

The TauRoast application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory. The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.

@@

Table~\ref{table:parrot_ptu} compares the time overhead of preserving the TauRoast application using Parrot and PTU.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
PTU accomplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.

@@

\begin{table}
\small
	\centering
	    \begin{tabular}{lcrr}
	        \hline
	        \bf Dependency Name & \bf Location & \bf Total Size &  \bf Used Size\\ 
	        \hline
	        CMSSW code     & CVS & 88.1GB &  5.2MB\\ \hline
	        Tau source       & Git & 73.7MB & 212KB \\ \hline
	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
	        .h file       & HTTP& 41KB & 0KB \\ \hline 
	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
	        Configuration & CVMFS & 7.4GB & 105MB \\ \hline
	        Linux commands & localFS & 110GB & 110MB \\ \hline     
	        HOME dir& AFS &12GB & 24MB\\ \hline
	        Misc commands & PanFS & 155TB & 8KB \\ \hline
	        Total      &    & 166.8TB     &  18GB \\ \hline
	    \end{tabular}
	    \normalsize
	    \caption{Data and Code Size Used by TauRoast}
	    \label{table:size-original-real}
\end{table}
%	\begin{tablenotes}
%	      \small
%	      \item The first column illustrates the total size of each data and software source; 
%	            the second column illustrates the size of the named files from each source;
%	            the third column illustrates the size of actually used data from each source.
%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
%	    \end{tablenotes}

>>>>

We evaluated the correctness and performance of running, packaging, and re-running the \emph{TauRoast} application using Parrot and PTU.
To do this, the application was first executed directly, its execution time and output were recorded. Then the application was executed under Parrot and PTU, and a self-contained package was created for each case. Finally, the application was re-executed using the package. The time overhead of each execution and re-execution was collected and compared with the recorded reference.

The \emph{TauRoast} application checks and evaluates a dataset with the size of 18 GB stored in HDFS, and can be finished in about 20 minutes when running directly on a server with 64 cores and 126 GB memory. The output of the application includes an event analysis log and a statistics information, and its size is 289 KB.

@@

Table~\ref{table:parrot_ptu} compares the time overhead of preserving the \emph{TauRoast} application using Parrot and PTU.
Parrot splits the packaging creation procedure into two sequential steps: first, execute the application within Parrot and generate the accessed file namelist; second, traverse the namelist and copy all the accessed files into a self-contained package.
PTU accomplishes the execution procedure and the package creation procedure concurrently through multi-threading, bringing 17.5\% additional time overhead.

@@

\begin{table}
\small
	\centering
	    \begin{tabular}{lcrr}
	        \hline
	        \bf Dependency Name & \bf Location & \bf Total Size &  \bf Used Size\\ 
	        \hline
	        CMSSW code     & CVS & 88.1GB &  5.2MB\\ \hline
	        Tau source       & Git & 73.7MB & 212KB \\ \hline
	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
	        .h file       & HTTP& 41KB & 0KB \\ \hline 
	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
	        Configuration & CVMFS & 7.4GB & 105MB \\ \hline
	        Linux commands & localFS & 110GB & 110MB \\ \hline     
	        HOME dir& AFS &12GB & 24MB\\ \hline
	        Misc commands & PanFS & 155TB & 8KB \\ \hline
	        Total      &    & 166.8TB     &  18GB \\ \hline
	    \end{tabular}
	    \normalsize
	    \caption{Data and Code Size Used by \emph{TauRoast}}
	    \label{table:size-original-real}
\end{table}
%	\begin{tablenotes}
%	      \small
%	      \item The first column illustrates the total size of each data and software source; 
%	            the second column illustrates the size of the named files from each source;
%	            the third column illustrates the size of actually used data from each source.
%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
%	    \end{tablenotes}

### 2015-01-15 tauroast.tex
Add citiation into Section 2

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS \cite{} cluster for data files, 
some configuration files were stored on a CVMFS \cite{} filesystem, and a variety of software tools were on an NFS \cite{}, PanFS\cite{} and AFS \cite{} systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.48\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fg:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.

>>>>

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS~\cite{borthakur2008hdfs} cluster for data files, 
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS~\cite{sandberg1985design}, PanFS~\cite{welch2008scalable} and AFS~\cite{howard1988scale} systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW)~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.
